\Large\textbf{Preparation GUIDE for Initial-Submission Manuscript}\\~\\ \large\textbf{ Preparation of Papers in Two-Column Format\\ for the ASP-DAC 2014 (\LaTeX2e version)}

### 2013-11-25 exps.tex
Updated table

{\renewcommand{\arraystretch}{0.9}
\begin{table}[t]
	\small
	\centering
	\caption{Program specification}
	\label{fig:benchlist}
	\scalebox{0.9}{
\begin{tabular}{cccc}
\toprule
\emph{Benchmark}       & \emph{Required delays} & \emph{\# of CDs} & 
\emph{Lines of code}        
\\ \midrule
HRTCS                  & 50.3-200.3 ms & 2                  & 56
\\ \midrule
\multirow{5}{*}{Motor} & 2.4 ms        & \multirow{5}{*}{1} & \multirow{5}{*}{116} \\ 
                       & 1.667 ms      &                    &                      \\ 
                       & 0.05 ms       &                    &                      \\ 
                       & 0.3 ms        &                    &                      \\ 
											 & 0.733 ms      &                    &
\\ \midrule
Printer                & TBC           & 2                  & 39
\\ \midrule
AECS/CD1               & 10000 ms      & -                  & 144
\\ \midrule
AECS/CD2               & 10000 ms      & -                  & 123
\\ \bottomrule
\end{tabular}
}
\vspace{-20pt}
\end{table}
}

{\renewcommand{\arraystretch}{0.6}
\begin{table}[t]
\twocolumn[
\centering
\begin{@twocolumnfalse}
	\caption{Actual delays obtained for \texttt{delay} constructs in the
benchmark programs based on their BCRT and WCRT}
\label{fig:comparison}
\begin{tabular}{ c  c  c  c  c  c  c }
	\toprule
	\multicolumn{2}{c}{}											& \emph{HRTCS} 		&
	\emph{Motor} 		  & \emph{Robot} 			  & \emph{AECS/CD1}   &
	\emph{AECS/CD2} \\ \midrule
	\multicolumn{2}{c}{\emph{BCRT}} 		&0.0334 ms 		& 0.0361 ms		  &
	0.0325 ms		  & 0.1683 ms		   & 0.1881 ms\\ \cmidrule(r){1-7}
	\multicolumn{2}{c}{\emph{WCRT}} 		&0.1120 ms 		& 0.1116 ms		  &
	0.0601 ms		  & 0.7147 ms		   & 1.0115 ms\\ \cmidrule(r){1-7}
								 \multirow{2}{*}{Delay 1}	 & M..N &50.3-200.3 ms 	& 2.4-7.4772 ms	  & 1230-2274.0263 ms & 10000-42473.2197 ms& 10000-53772.0045 ms \\ \cmidrule(r){2-7}
											   & d			 		&1506-1787  	& 67 			  & 37861			  & 59427		       &53160\\ \cmidrule(r){1-7}
								 \multirow{2}{*}{Delay 2}	 & M..N & 	N/A 		& 1.667-5.2452 ms & N/A				  & N/A 			   &10000-53772.0045 ms\\ \cmidrule(r){2-7}
											   & d			 		& 	N/A	 		& 47			  & N/A				  & N/A       		   &53160\\ \cmidrule(r){1-7}
								 \multirow{2}{*}{Delay 3}	 & M..N & 	N/A	 		& 0.05-0.2232 ms  & N/A				  & N/A       		   &N/A\\ \cmidrule(r){2-7}
											   & d			 		& 	N/A	 		& 2		      	  &	N/A				  & N/A       		   &N/A\\ \cmidrule(r){1-7}
								 \multirow{2}{*}{Delay 4}	 & M..N & 	N/A	 		& 0.3-1.0044 ms   & N/A				  &	N/A       		   &N/A\\ \cmidrule(r){2-7}
											   & d				 	& 	N/A	 		& 9				  & N/A				  &	N/A      		   &N/A\\ \cmidrule(r){1-7}
								 \multirow{2}{*}{Delay 5}	 & M..N & 	N/A	 		& 0.733-2.3436 ms & N/A				  &	N/A      		   &N/A\\ \cmidrule(r){2-7}
											   & d			 		& 	N/A	 		& 21 			  &	N/A
												 & N/A      		   &N/A\\ \bottomrule
\end{tabular}
\end{@twocolumnfalse}
]
\end{table}
}

We have carried out a number of experiments on a set of applications
with real-time constraints. The characteristics of the benchmark set
including delay specifications are shown in Table~\ref{fig:benchlist}.

@@

\begin{figure}[h!]
	\begin{SubFloat}{\label{delaycode:a}}
		\centering
		\begin{minipage}[b]{0.3\linewidth}
			\scriptsize
\begin{verbatim}
emit TimerTriggered;
trap(T){
  abort(DoorOpened){
    await(TimeOut);
    exit(T); 
  }
}
\end{verbatim}
		\end{minipage}
	\end{SubFloat}
\hspace{1cm}%
	\begin{SubFloat}{\label{delaycode:b}}
		\centering
		\begin{minipage}[b]{0.5\linewidth}
			\scriptsize
\begin{verbatim}
// No emit statement
trap(T){
  abort(DoorOpened){
    delay(2.4 ms);
    exit(T);  
  }
}
\end{verbatim}
		\end{minipage}
	\end{SubFloat}
\caption{Replacing external timer with delay construct}
\label{delaycode}
\end{figure}

Motor is a stepper motor controller from~\cite{Bourke2009a}, used for
producing monochrome images on paper by applying a correct application
of current to the print head (a row of resistors). In this example,
duration of current applied to the print head is controlled based on
feedback logic using real-time delays which are expressed in Esterel
constructs. We have rewritten the program in SystemJ and compared
between desired and relaxed delay according to WCRT and BCRT of the
program.  Printer is an example from [], which models a printer and a
spooler in timed CSP. Their operation is rather simple: as soon as the
spooler receives a print job, passes it to the printer through channel
for processing. The example demonstrates that by specifying delay bounds
(e.g. 1 to 5 time units) between two subsequent behaviors, the job is
passed along the channel as soon as both processes become ready.

@@

HRTCS consists of 2 CDs, but only one with real-time delays. AECS also
has 2 CDs; CD1 consist of a single delay statement, while CD2 has 2
delay statements. In this case, as explained previously, delay
statements replace the external timers and corresponding interface
signals. The system triggers an alarm 10 seconds after detection of an
intruder or generates a beep sound when an entrance door is being opened
for the same amount of time. In Printer, each spooler and printer
process is mapped to a single clock-domain. Spooler CD sends a job to
the Printer CD between [] to [] ms after receiving it from the
enviornment (e.g. a user). On the other hand, Printer CD notifies
environment that it starts printing between [] to [] ms once it receives
the job from the Spooler CD. Actual print job is started between [] to
[] after the notification. In this example, bounded delay ensures that
both channel communication and print job should occur within the
specified amount of time. Lastly, Motor is a synchronous program with 5
delay statements where they controls amount of current into the stepper
motor coils.

@@

We use the \textit{Java Optimized Processor}
(JOP)~\cite{jop:jnl:jsa2007}, to carry out all our experiments. JOP
implements the JVM specification in hardware directly, and has been
shown to be real-time amenable. We statically estimate the WCRT and BCRT
of these benchmark applications using the real-time analysis tools
provided by the JOP design framework. The \textit{Safety Critical Java}
(SCJ) specification we use for real-time analysis avoids garbage
collection (GC) and hence, GC overheads and unpredictability are
completely avoided. Note that only HRTCS and Printer have
non-deterministic delays (\texttt{M..N}) as their program specification
where others use exact delays (\texttt{M}). The actual delay after
applying relaxation for the upper real-time bound is shown in
Table~\ref{fig:comparison}.

@@

%As one can see in Table \ref{fig:comparison}, 
As a first step, BCRT and WCRT were calculated for all examples. Given
the real-time \mbox{\texttt{delay (M..N)}} provided by programmers,
required logical delay \texttt{d} was determined by applying
Algorithm~\ref{alg:1}. In HRTCS, real-time delay of the range
50.3..200.3 (ms) is only satisfied when \emph{d} is between 1506 and
1787 (as shown previously in
Section~\ref{sec:intr-real-time}~\ref{sec:find-logic-delay}).  It is
then compiler's job to statically choose one of the values in this
range.

% The upper bound \texttt{N} needed to be relaxed for all examples other
% than HRTCS to obtain a feasible \texttt{d}. Therefore,
On the other hand, Algorithm \ref{alg:2} is applied to those examples,
where relaxation was required, to determine the minimum upper real-time
bound \emph{N} such that there exist a solution for \emph{D} in
Algorithm \ref{alg:1}. This algorithm gives a unique number for logical
tick delay \emph{d} such that \emph{d} = Min(\emph{$S_2$}) =
Max(\emph{$S_1$}).  The compiler, therefore, will choose \emph{d} based
on the newly computed \emph{N} for the examples: Printer, Motor and
AECS.

>>>>

{\renewcommand{\arraystretch}{0.9}
\begin{table}[t]
	\small
	\centering
	\caption{An overview of the benchmark programs}
	\label{fig:benchlist}
	\scalebox{0.9}{
		\begin{tabular}{llp{0.5cm}p{1cm}}
\toprule
\emph{Benchmark}       & \emph{Delay constructs used in each CD} & \emph{\# of CDs} & 
\emph{Lines of code}        
\\ \midrule
HRTCS                  & \texttt{delay(50.3..200.3 ms)} ($CD1$) & 2                  & 56
\\ \midrule
\multirow{5}{*}{Motor} & \texttt{delay(2.4..2.4 ms)}        & \multirow{5}{*}{1} & \multirow{5}{*}{116} \\ 
											 & \texttt{delay(1.667..1.667 ms)}      &                    &                      \\ 
											 & \texttt{delay(0.05..0.05 ms)}       &                    &                      \\ 
											 & \texttt{delay(0.3..0.3 ms)}        &                    &                      \\ 
											 & \texttt{delay(0.733..0.733 ms)}      &                    &
\\ \midrule
\multirow{3}{*}{Printer}
& \texttt{delay(2.7..10.6 ms)} ($CD1$)      & \multirow{3}{*}{2}        & \multirow{3}{*}{39} \\
& \texttt{delay(1.2..30.3 ms)} ($CD2$)		  &														&											\\
& \texttt{delay(5.6..100.2 ms)} ($CD2$)     &														&											
\\ \midrule
\multirow{2}{*}{AECS} & \texttt{delay(10000 ms)} ($CD1$) 
& \multirow{2}{*}{2} & \multirow{2}{*}{267} \\
& \texttt{delay(10000..10000 ms)} ($CD2$) & &
\\ \bottomrule
\end{tabular}
}
\vspace{-20pt}
\end{table}
}

{\renewcommand{\arraystretch}{0.6}
\begin{table}[t]
\twocolumn[
\centering
\begin{@twocolumnfalse}
	\caption{Actual delays obtained for \texttt{delay} constructs in the
benchmark programs based on their BCRT and WCRT}
\label{fig:comparison}
\begin{tabular}{ c c l l l l l l }
	\toprule
	\multicolumn{2}{c}{} & \emph{HRTCS} & \emph{Motor} & \emph{Printer/CD1} &
	\emph{Printer/CD2} & \emph{AECS/CD1} &	\emph{AECS/CD2} \\ 
	\midrule
	\multicolumn{2}{c}{\emph{BCRT}}	& 0.0334 ms	& 0.0361 ms & 0.009613 ms &
	0.0263 ms & 0.1683 ms & 0.1881 ms\\ 
	\cmidrule(r){1-8}
	\multicolumn{2}{c}{\emph{WCRT}} &0.1120 ms & 0.1116 ms & 0.0603 ms
	& 0.0491 ms & 0.8148 ms & 1.0115 ms\\ 
	\cmidrule(r){1-8}

	\multirow{2}{*}{Delay 1} & M..N & 50.3-200.3 ms	& 2.4-8.4882 ms	  &
	2.7-16.9378 ms & 1.2-30.3 ms & 10000-42483.2198 ms& 10000-53882.0045 ms \\
	\cmidrule(r){2-8}
	& d &1506-1888 & 68 & 281 & 46-617 & 59428 &53160\\ 
	\cmidrule(r){1-8}
	\multirow{2}{*}{Delay 2} & M..N & N/A & 1.668-5.2452 ms & N/A &
	5.6-100.2 ms & N/A &10000-53882.0045 ms\\ 
	\cmidrule(r){2-8}
	& d & N/A & 48 & N/A & 213-2041 & N/A &53160\\ 
	\cmidrule(r){1-8}
	\multirow{2}{*}{Delay 3} & M..N & N/A & 0.05-0.2232 ms & N/A & N/A & N/A
	&N/A\\ 
	\cmidrule(r){2-8}
	& d & N/A & 2 & N/A & N/A & N/A &N/A\\ 
	\cmidrule(r){1-8}
	\multirow{2}{*}{Delay 4} & M..N & N/A & 0.3-1.0044 ms & N/A & N/A & N/A
	&N/A\\ 
	\cmidrule(r){2-8}
	& d & N/A & 9 & N/A & N/A & N/A &N/A\\ 
	\cmidrule(r){1-8}
	\multirow{2}{*}{Delay 5} & M..N & N/A & 0.833-2.3436 ms & N/A & N/A & N/A
	&N/A\\ 
	\cmidrule(r){2-8}
	& d & N/A & 21 & N/A
	& N/A & N/A &N/A\\ \bottomrule
\end{tabular}
\end{@twocolumnfalse}
]
\end{table}
}

We have carried out a number of experiments on a set of applications
with real-time constraints. The characteristics of the benchmark set
including required real-time delays and program sizes are shown in
Table~\ref{fig:benchlist}.

@@

\begin{figure}[h!]
	\begin{SubFloat}{\label{delaycode:a}}
		\centering
		\begin{minipage}[b]{0.3\linewidth}
			\scriptsize
\begin{verbatim}
emit TimerTriggered;
trap(T){
  abort(DoorOpened){
    await(TimeOut);
    exit(T); 
  }
}
\end{verbatim}
		\end{minipage}
	\end{SubFloat}
\hspace{1cm}%
	\begin{SubFloat}{\label{delaycode:b}}
		\centering
		\begin{minipage}[b]{0.5\linewidth}
			\scriptsize
\begin{verbatim}
// No emit statement
trap(T){
  abort(DoorOpened){
    delay(10000 ms);
    exit(T);  
  }
}
\end{verbatim}
		\end{minipage}
	\end{SubFloat}
\caption{Replacing external timer with delay construct}
\label{delaycode}
\end{figure}

Motor is a stepper motor controller from~\cite{Bourke2009a}, used for
producing monochrome images on paper by applying a correct application
of current to a print head (a row of resistors). In this example,
duration of current applied is controlled by the feedback logic using
real-time delays which are expressed in Esterel constructs. We have
rewritten the program in SystemJ and compared between desired and
relaxed delays according to WCRT and BCRT of the program. Printer is an
example from [], which models a printer and a spooler in timed CSP.
Their operation is rather simple: as soon as the spooler receives a
print job, passes it to the printer through a channel where actual
printing process take place. The example demonstrates that by specifying
delay bounds (e.g. 1 to 5 time units) on receiving and sending channel
ends data exchange will occur as soon as both processes become ready.

@@

HRTCS consists of 2 CDs, but only one with real-time delays. AECS also
has 2 CDs; CD1 consist of a single delay statement, while CD2 has 2
delay statements. In this case, as explained previously, delay
statements replace the external timers and corresponding interface (I/O)
signals. The system triggers an alarm 10 seconds after detection of an
intruder or generates a beep sound when an entrance door is being opened
for the same amount of time. In Printer, each spooler and printer
process is mapped to a single clock-domain. Spooler CD sends a job to
the Printer CD between [] to [] ms after receiving it from the
enviornment (e.g. a user). On the other hand, Printer CD notifies
environment that it starts printing between [] to [] ms once it receives
the job from the Spooler CD. Actual print job is started between [] to
[] after the notification. In this example, bounded delay ensures that
both channel communication and print job should occur within the
specified amount of time. Lastly, Motor is a synchronous program with 5
delay statements where they controls amount of current into the stepper
motor coils.

@@

We use the \textit{Java Optimized Processor}
(JOP)~\cite{jop:jnl:jsa2007}, to carry out all our experiments. JOP
implements the JVM specification in hardware directly, and has been
shown to be real-time amenable. We statically estimate the WCRT and BCRT
of these benchmark applications using the real-time analysis tools
provided by the JOP design framework. The \textit{Safety Critical Java}
(SCJ) specification we use for real-time analysis avoids garbage
collection (GC) and hence, GC overheads and unpredictability are
completely avoided.

@@

Table~\ref{fig:comparison} shows the result of our algorithm applied to
each benchmark program. Note that we allowed the compiler to find the
minimum upper real-time bounds for all delay constructs, e.g. bounded
(\texttt{M..N}) or exact (\texttt{M..M}) delays, when it fails to find a
feasible solution. However, a user can prohibit this behavior through
configuration that such case is an error.

As a first step, BCRT and WCRT were calculated for all examples. Given
the real-time \mbox{\texttt{delay (M..N)}} provided by programmers,
required logical delay \textit{d} was determined by applying
Algorithm~\ref{alg:1}. In HRTCS, real-time delay of the range
50.3..200.3 (ms) is only satisfied when \emph{d} is between 1506 and
1787 (as shown previously in
Section~\ref{sec:intr-real-time}~\ref{sec:find-logic-delay}). Similarly,
Printer/CD2 satisfies real-time ranges of 1.2..30.3 (ms) and 5.6..100.2
(ms) when \emph{d} is 46..617 and 213..2041 respectively. It is then
compiler's job to statically choose one of the values in this range.

% The upper bound \texttt{N} needed to be relaxed for all examples other
% than HRTCS to obtain a feasible \texttt{d}. Therefore,
On the other hand, Algorithm \ref{alg:2} is applied to those examples,
where relaxation was required, to determine the minimum upper real-time
bound \emph{N} such that there exist a solution for \emph{D} in
Algorithm \ref{alg:1}. This algorithm gives a unique number for logical
tick delay \emph{d} such that \emph{d} = Min(\emph{$S_2$}) =
Max(\emph{$S_1$}).  The compiler, therefore, will choose \emph{d} based
on the newly computed \emph{N} for the examples: Printer/CD1, Motor and
AECS.
